Scalar on Function Regression

### 2022-01-07 Presentation/slides.tex
Correction
Update

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the dimension of the domain of our function is 1
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If $f, g \in \mathbb{L}^{2}$,
		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		, where $a$ and $b$ are scalars. (Maybe don't need)\\
		We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		\begin{itemize}
			\item Orthogonolality of two different functions
			\item Distance between functions
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Plots}
		point plots to link basis expansion
	\end{frame}
	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

>>>>

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If $f, g \in \mathbb{L}^{2}[0,1]$,
		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		, where $a$ and $b$ are scalars. (Maybe don't need)\\
		We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		\begin{itemize}
			\item Orthogonolality of two different functions
			\item Distance between functions
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Data Generating Process}
		With $X_{i}(t_{ij}) \in \mathbb{L}^{2}[0,1]$, the measurement of $X_{ij}$ is assumed to have noise with $\mathbb{E}(\epsilon)_{ij}=0$ and $\textbf{Var}(\epsilon_{ij}^{2})$, which are independent across $i$ and $j$.\\
		When the functional data has the same grid of domain, (SKIP)	
	\end{frame}

	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}
